---
title: "Analysis of Film and Music Sales for Media Distributors, Inc."
author: "Tejas Adhikari"
date: "Spring 2025"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    theme: paper
    highlight: tango
subtitle: Prepared by Oakland Partners
---


```{r dependenciesBlock, echo = F, warning = F, message = F}
# Install RSQLite package if not installed already
# This makes the code portable
if("RSQLite" %in% rownames(installed.packages()) == FALSE) {
  install.packages("RSQLite")
}
# Load RSQLite Library
library(RSQLite)

# Install DBI package if not installed already
# This makes the code portable
if("DBI" %in% rownames(installed.packages()) == FALSE) {
  install.packages("DBI")
}
library(DBI)

# Install kableExtra package if not installed already
# This makes the code portable
if("kableExtra" %in% rownames(installed.packages()) == FALSE) {
  install.packages("kableExtra")
}
library(kableExtra)


# Connect to MySQL DB 
# Set up connection parameters.
db_user <- ''
db_password <- ''
db_name <- ''
db_host <- ''
db_port <- 16950  
  
# Connect to MySQL DB
conn <- dbConnect(RMySQL::MySQL(), 
                  user = db_user, 
                  password = db_password, 
                  dbname = db_name, 
                  host = db_host, 
                  port = db_port)

```

## Background

Media Distributors, Inc. is a Wichita, KY based distributor and seller of films and music for commercial purposes. For the past few years, it has managed its film and music sales separately using different applications. This division is historical as Media Distributors started distributing films and then acquired SoundMania about two years ago. As the two distribution channels were different, CTO Alvin Coelho made the decision not to integrate the SoundMania’s information systems and database with those of Media Distributors. This has not been a problem until now, however Media Distributors intends to make itself available for acquisition. To that end, an integrated view of the business, particularly sales, is needed.

This report provides key sales, revenue, and customer metrics to showcase Media Distributors business. The analysis provided is based on data from a custom-built datamart containing data extracted from two operational databases.

We have maintained the address of the customers and not the stores as the last paragraph mentions the foloowing for the whole report "The customer base is concentrated in India, China, and United States, which also serve as the top-performing markets." an this can be achieved by using the customers address for country.


## Key Business Metrics

This sections provides key revenue and customer information segmented by time, country, and business unit. Revenue numbers are in US$.



### Sales Revenue



```{r getHighestSalesBlock, echo = F, warning = F, message = F}
# Get the Year with the highest sales.
sql <- "SELECT 
        	SUM(sf.MonthlyUnitsSold) AS UnitsPerYear,
        	ROUND(SUM(sf.MonthlyRevenue), 0) AS RevenuePerYear,
          pd.YEAR
        FROM SalesFacts sf
        INNER JOIN PeriodDimension pd 
        		ON sf.PeriodId = pd.id
        GROUP BY pd.YEAR
        ORDER BY UnitsPerYear DESC
        LIMIT 1;"
HighestSalesData <- dbGetQuery(conn, sql) 

# Get teh Highest sales by Country and by Year.
sql <- "SELECT 
        	SUM(sf.MonthlyUnitsSold) AS UnitsPerCountry,
          ROUND(SUM(sf.MonthlyRevenue), 0) AS RevenuePerCountry,
          pd.YEAR,
          cd.Country
        FROM SalesFacts sf
        INNER JOIN PeriodDimension pd
        	ON sf.PeriodId = pd.id
        INNER JOIN CountryDimension cd 
        	ON sf.CountryId = cd.id
        GROUP BY cd.Country, pd.YEAR
        ORDER BY UnitsPerCountry DESC
        LIMIT 2;"
HighestSalesDataCountryYear <- dbGetQuery(conn, sql)

# Get the most recent two years.
sql <- "SELECT 
        	DISTINCT YEAR
        FROM PeriodDimension
        ORDER BY YEAR DESC
        LIMIT 2;"
recentTwoYears <- dbGetQuery(conn, sql)
# Store the most recent 2 years
year1 <- recentTwoYears$YEAR[1]  
year2 <- recentTwoYears$YEAR[2]
```

The year with the most sales was `r HighestSalesData$YEAR` with a total revenue across both business units of \$`r format(HighestSalesData$RevenuePerYear, big.mark = ",")`. The country with the most sales was `r HighestSalesDataCountryYear$Country[1]` with total sales across both business units in `r HighestSalesDataCountryYear$YEAR[1]` of \$`r format(HighestSalesDataCountryYear$RevenuePerCountry[1], big.mark = ",")`. It was followed by the `r HighestSalesDataCountryYear$Country[2]` with \$`r format(HighestSalesDataCountryYear$RevenuePerCountry[2], big.mark = ",")`.

The table below shows sales revenue by country and ordered by total sales for the two most recent years, `r year2` and `r year1` The table is restricted to the top five countries with the most sales. The column ‘Total’ in the table represents the total for all years for which there is data and not just the past two years.



```{r yearlyRevenueTable, echo = F, warning = F, message = F}

# Get the top 5 countries with the highest total revenue in sales.
sql <- "SELECT 
          ROUND(SUM(sf.MonthlyRevenue), 0) AS RevenuePerCountry,
          cd.Country
        FROM SalesFacts sf
        INNER JOIN CountryDimension cd 
        	ON sf.CountryId = cd.id
        GROUP BY cd.Country
        ORDER BY RevenuePerCountry DESC
        LIMIT 5;"
countries <- dbGetQuery(conn, sql)

country1 <- countries$Country[1]
country2 <- countries$Country[2]
country3 <- countries$Country[3]
country4 <- countries$Country[4]
country5 <- countries$Country[5]


# Get the table for top 5 countries revenue data for the most recent 2 years 
# and total revenue.
sql <- sprintf("
                SELECT
                  cd.Country,
                  ROUND(SUM(CASE WHEN pd.YEAR = '%d' THEN sf.MonthlyRevenue ELSE 0 END), 0) AS '%d',
                  ROUND(SUM(CASE WHEN pd.YEAR = '%d' THEN sf.MonthlyRevenue ELSE 0 END), 0) AS '%d',
                  ROUND(SUM(sf.MonthlyRevenue), 0) AS `Total (All Years)`
                FROM SalesFacts sf
                INNER JOIN PeriodDimension pd ON sf.PeriodId = pd.id
                INNER JOIN CountryDimension cd ON sf.CountryId = cd.id
                WHERE cd.Country IN ('%s', '%s', '%s', '%s', '%s')
                GROUP BY cd.Country
                ORDER BY `Total (All Years)` DESC;
               ", year2, year2, year1, year1, country1, country2, country3, country4, country5)
tableResult <- dbGetQuery(conn, sql)

# Format to put in ',' for long numbers
tableResultFormatted <- tableResult
cols <- names(tableResultFormatted)[2:4]

for (col in cols) {
  tableResultFormatted[[col]] <- format(tableResultFormatted[[col]], big.mark = ",", scientific = FALSE)
}


# Create and display a formatted table using kableExtra
tableResultFormatted %>%
  kbl(col.names = c("", year2, year1, "Total (All Years)"),
      caption = "Total Revenue For Top Five Countries For Most Recent Two Years",
      align = "c") %>%
  add_header_above(setNames(4, "Revenue Per Year")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE) %>%
  row_spec(0, bold = TRUE, font_size = 14) %>%  # Header row styling
  column_spec(1, bold = TRUE)        

```


```{r getYearsInDB, echo = F, warning = F, message = F}

# Get all the years for which data is present in the DBs
sql <- "SELECT 
          	DISTINCT YEAR
          FROM PeriodDimension
          ORDER BY YEAR ASC;"
years <- dbGetQuery(conn, sql)
firstYear <- years$YEAR[1]
lastYear <- tail(years$YEAR, 1)
totalYears <- nrow(years)
```


The table below shows the revenue broken down by quarter for the top five countries. It shows the total revenue for each quarter across all business units and years. So, for example, the column “Q1” is the total sales for music and film for all years for which there is data, which is from `r firstYear` to `r lastYear`.


```{r quarterlyRevenueTable, echo = F, warning = F, message = F}

# Get the table for top 5 countries revenue data for all the years' quarters
# and Average revenue.
sql <- sprintf("
                SELECT 
                  cd.Country,
                  ROUND(SUM(CASE WHEN pd.Quarter = 1 THEN sf.MonthlyRevenue ELSE 0 END), 0) AS Q1,
                  ROUND(SUM(CASE WHEN pd.Quarter = 2 THEN sf.MonthlyRevenue ELSE 0 END), 0) AS Q2,
                  ROUND(SUM(CASE WHEN pd.Quarter = 3 THEN sf.MonthlyRevenue ELSE 0 END), 0) AS Q3,
                  ROUND(SUM(CASE WHEN pd.Quarter = 4 THEN sf.MonthlyRevenue ELSE 0 END), 0) AS Q4,
                  ROUND(SUM(sf.MonthlyRevenue) / %d, 0) AS Average
                FROM SalesFacts sf
                INNER JOIN PeriodDimension pd ON sf.PeriodId = pd.id
                INNER JOIN CountryDimension cd ON sf.CountryId = cd.id
                WHERE cd.Country IN ('%s', '%s', '%s', '%s', '%s')
                GROUP BY cd.Country
                ORDER BY Average DESC;
              ", totalYears, country1, country2, country3, country4, country5)
tableResult <- dbGetQuery(conn, sql)

# Format to put in ',' for long numbers
tableResultFormatted <- tableResult
cols <- names(tableResultFormatted)[2:6]

for (col in cols) {
  tableResultFormatted[[col]] <- format(tableResultFormatted[[col]], big.mark = ",", scientific = FALSE)
}


# Create and display a formatted table using kableExtra
tableResultFormatted %>%
  kbl(col.names = c("", "Q1", "Q2","Q3", "Q4", "Average"),
      caption = "Cumulative and Average Quarterly Revenue",
      align = "c") %>%
  add_header_above(setNames(6, sprintf("Quarterly Revenue %s to %s", firstYear, lastYear))) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE) %>%
  row_spec(0, bold = TRUE, font_size = 14) %>%  # Header row styling
  column_spec(1, bold = TRUE)        

```


```{r getTop5Countries, echo = F, warning = F, message = F}
# Get the total number of customers.
sql <- "SELECT
        	SUM(CustomerCount) AS totalCustomers
        FROM CustomerFacts;"
totalCustomers <- dbGetQuery(conn, sql)


# Get the total number of countries
sql <- "SELECT
        	COUNT(*) AS totalCountries
        FROM CountryDimension;"
totalCountries <- dbGetQuery(conn, sql)

# Get the top 5 countries with majority of the customers.
sql <- "SELECT
        	cd.Country,
        	SUM(cf.CustomerCount) AS totalCustomersPerCountry
        FROM CustomerFacts cf
        INNER JOIN CountryDimension cd
        	ON cf.CountryId = cd.id
        GROUP BY cd.Country
        ORDER BY totalCustomersPerCountry DESC
        LIMIT 5;"
top5Countries <- dbGetQuery(conn, sql)

customerCountry1 <- top5Countries$Country[1]
customerCountry2 <- top5Countries$Country[2]
customerCountry3 <- top5Countries$Country[3]
customerCountry4 <- top5Countries$Country[4]
customerCountry5 <- top5Countries$Country[5]

```


### Customer Distribution

Across both business units, there are `r format(totalCustomers$totalCustomers, big.mark = ",")` customers in `r format(totalCountries$totalCountries, big.mark = ",")` different countries, with the majority of customers in `r customerCountry1`, `r customerCountry2`, and `r customerCountry3`


```{r getCustomersByBznzUnitTable, echo = F, warning = F, message = F}
# Get the table for top 5 countries revenue data for all the years' quarters
# and Average revenue.
sql <- sprintf("
                SELECT 
                  cd.Country,
                  SUM(CASE WHEN cf.Type = 'Film' THEN cf.CustomerCount ELSE 0 END) AS Film,
                  SUM(CASE WHEN cf.Type = 'Music' THEN cf.CustomerCount ELSE 0 END) AS Music,
                  SUM(cf.CustomerCount) AS Total
                FROM CustomerFacts cf
                INNER JOIN CountryDimension cd ON cf.CountryId = cd.id
                WHERE cd.Country IN ('%s', '%s', '%s', '%s', '%s')
                GROUP BY cd.Country
                ORDER BY Total DESC;
              ", customerCountry1, customerCountry2, customerCountry3, customerCountry4, customerCountry5)
tableResult <- dbGetQuery(conn, sql)

# Format to put in ',' for long numbers
tableResultFormatted <- tableResult
cols <- names(tableResultFormatted)[2:4]

for (col in cols) {
  tableResultFormatted[[col]] <- format(tableResultFormatted[[col]], big.mark = ",", scientific = FALSE)
}


# Create and display a formatted table using kableExtra
tableResultFormatted %>%
  kbl(col.names = c("", "Film", "Music", "Total"),
      caption = "Customers by Business Unit",
      align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE) %>%
  row_spec(0, bold = TRUE, font_size = 14) %>%  # Header row styling
  column_spec(1, bold = TRUE)        

```



### Film vs Music Revenue

Sales fluctuate over time and the table below shows total revenue per month for the years for which we have data.

```{r getRevenueByYearBznzUnitTable, echo = F, warning = F, message = F}
# Get the film and music revenue by year and business unit.
sql <- "SELECT 
          sf.Type AS `Business Unit`,
          pd.Year,
          ROUND(SUM(sf.MonthlyRevenue), 0) AS Revenue
        FROM SalesFacts sf
        JOIN PeriodDimension pd ON sf.PeriodId = pd.id
        GROUP BY sf.Type, pd.Year
        ORDER BY sf.Type, pd.Year;"
filmMusicRevenue <- dbGetQuery(conn, sql)

# Pivot the filmMusicRevenue table
filmMusicRevenuePivot <- reshape(
  filmMusicRevenue,
  idvar = "Business Unit",
  timevar = "Year",
  direction = "wide"
)
# Replace NA values to '0'
filmMusicRevenuePivot[is.na(filmMusicRevenuePivot)] <- 0


# Create and display a formatted table using kableExtra
filmMusicRevenuePivot %>%
  kbl(row.names = FALSE, # Suppress row indices
      col.names = c("", "2005", "2006", "2009", "2010", "2011", "2012", "2013"),
      caption = "Revenue by year and business unit",
      align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE) %>%
  row_spec(0, bold = TRUE, font_size = 14) %>%  # Header row styling
  column_spec(1, bold = TRUE)        
```

The graph below illustrates the quarterly growth of the film and music business over the past years for which we have data.

```{r getLineGraph, echo = F, warning = F, message = F}
# Get the film and music revenue data per year per quarter.
sql <- "SELECT 
          sf.Type AS `Business Unit`,
          pd.Year,
          pd.Quarter,
          ROUND(SUM(sf.MonthlyRevenue), 0) AS Revenue
        FROM SalesFacts sf
        INNER JOIN PeriodDimension pd ON sf.PeriodId = pd.id
        GROUP BY sf.Type, pd.Year, pd.Quarter
        ORDER BY pd.Year, pd.Quarter;"
filmMusicQuarterlyRevenue <- dbGetQuery(conn, sql)

# Split into Film and Music data
filmData <- filmMusicQuarterlyRevenue[filmMusicQuarterlyRevenue$`Business Unit` == "Film", ]
musicData <- filmMusicQuarterlyRevenue[filmMusicQuarterlyRevenue$`Business Unit` == "Music", ]

# Add Labels for the x axis in the graph to the Data
filmData$Label <- paste(filmData$Year, paste0("Q", filmData$Quarter))
musicData$Label <- paste(musicData$Year, paste0("Q", musicData$Quarter))

# Combine the labels in filmData and musicData and sort them
allLabels <- unique(c(filmData$Label, musicData$Label))
allLabels <- sort(allLabels)

# create the vector for the revenue for film and music, setting to NA to just define the vectors.
filmRevenue <- rep(NA, length(allLabels))
musicRevenue <- rep(NA, length(allLabels))

# Fill the vectors with actual values based on the allLabels from the respective data
filmRevenue[match(filmData$Label, allLabels)] <- filmData$Revenue
musicRevenue[match(musicData$Label, allLabels)] <- musicData$Revenue

# Plot the graph
x <- seq_along(allLabels)

plot(x, filmRevenue,
     type = "o", col = "red", pch = 16, lty = 1,
     xaxt = "n", xlab = "Quarter", ylab = "Revenue ($)",
     main = "Revenue Comparison By Business Unit",
     ylim = range(c(filmRevenue, musicRevenue), na.rm = TRUE))

lines(x, musicRevenue, type = "o", col = "blue", pch = 16, lty = 1)

axis(1, at = x, labels = allLabels, las = 2, cex.axis = 0.7)

legend("topright", legend = c("Film", "Music"),
       col = c("red", "blue"), pch = 16, lty = 1)

```

In terms of units sold, the table below sheds light on this by country and by business unit.

```{r unitsSoldByCountryTable, echo = F, warning = F, message = F}
# Get the top 3 countries with maximux units sold
sql <- "SELECT
        	cd.Country,
        	SUM(sf.MonthlyUnitsSold) AS totalUnitsSold
        FROM SalesFacts sf
        INNER JOIN CountryDimension cd
        	ON sf.CountryId = cd.id
        GROUP BY cd.Country
        ORDER BY totalUnitsSold DESC
        LIMIT 3;"
top3Countries <- dbGetQuery(conn, sql)
# Store teh countries
unitsCountry1 <- top3Countries$Country[1]
unitsCountry2 <- top3Countries$Country[2]
unitsCountry3 <- top3Countries$Country[3]


# Query to get units sold per quarter by country
sql <- sprintf("SELECT 
                  cd.Country,
                  pd.Year,
                  pd.Quarter,
                  SUM(sf.MonthlyUnitsSold) AS Units
                FROM SalesFacts sf
                INNER JOIN PeriodDimension pd ON sf.PeriodId = pd.Id
                INNER JOIN CountryDimension cd ON sf.CountryId = cd.Id
                WHERE cd.Country IN ('%s', '%s', '%s')
                GROUP BY cd.Country, sf.Type, pd.Year, pd.Quarter
                ORDER BY cd.Country, pd.Year, pd.Quarter;",
               country1, country2, country3)
unitSales <- dbGetQuery(conn, sql)


# create a function to build the table for a given country and data
build_country_table <- function(data, country) {
  # Filter data for the given country
  df <- data[data$Country == country, ]
  
  # Get unique years and quarters
  years <- sort(unique(df$Year))
  quarters <- paste0("Q", 1:4)
  
  # Initialize empty matrix with Q1-Q4, Total, Average rows and years, Total and Average cols
  table_matrix <- matrix(0, nrow = 6, ncol = length(years) + 2)
  rownames(table_matrix) <- c(quarters, "Total", "Average")
  colnames(table_matrix) <- c(as.character(years), "Total", "Average")
  
  # Fill in values
  for (i in seq_along(years)) {
    yr <- years[i]
    for (q in 1:4) {
      val <- df$Units[df$Year == yr & df$Quarter == q]
      if (length(val) > 0) {
        table_matrix[q, i] <- val
      }
    }
  }
  
  # Compute row totals and averages
  table_matrix["Total", 1:length(years)] <- colSums(table_matrix[1:4, 1:length(years)])
  table_matrix["Average", 1:length(years)] <- round(table_matrix["Total", 1:length(years)] / 4)
  
  # Compute column totals and averages
  table_matrix[1:4, "Total"] <- rowSums(table_matrix[1:4, 1:length(years)])
  table_matrix[1:4, "Average"] <- round(rowMeans(table_matrix[1:4, 1:length(years)]))
  
  # Final total and average
  table_matrix["Total", "Total"] <- sum(table_matrix[1:4, 1:length(years)])
  table_matrix["Average", "Total"] <- round(table_matrix["Total", "Total"] / 4)
  
  table_matrix["Total", "Average"] <- round(mean(table_matrix["Total", 1:length(years)]))
  table_matrix["Average", "Average"] <- round(mean(table_matrix["Average", 1:length(years)]))
  
  return(table_matrix)
}

# Generate tables for top 3 countries in units sold
table1 <- build_country_table(unitSales, unitsCountry1)
table2 <- build_country_table(unitSales, unitsCountry2)
table3 <- build_country_table(unitSales, unitsCountry3)


# Get the union of all year columns across the tables
allYears <- unique(c(colnames(table1)[-c(ncol(table1)-1, ncol(table1))], 
                     colnames(table2)[-c(ncol(table2)-1, ncol(table2))], 
                     colnames(table3)[-c(ncol(table3)-1, ncol(table3))]))

# Add "Total" and "Average" columns back to the list
allYears <- c(allYears, "Total", "Average")


# Function to ensure all tables have the same columns and fill missing values with 0
fill_missing_years <- function(table, allYears) {
  # Create a new matrix with allYears as columns and rows preserved
  expandedTable <- matrix(0, nrow = nrow(table), ncol = length(allYears),
                          dimnames = list(rownames(table), allYears))
  
  # Copy existing values from the original table
  colnamesMatch <- intersect(colnames(table), allYears)
  expandedTable[, colnamesMatch] <- table[, colnamesMatch]
  
  return(expandedTable)
}

# Expand tables to include all year columns
table1 <- fill_missing_years(table1, allYears)
table2 <- fill_missing_years(table2, allYears)
table3 <- fill_missing_years(table3, allYears)


# print(table1)
# print(table2)
# print(table3)

# Convert each matrix to a data frame with Country as a column
df1 <- as.data.frame(table1, stringsAsFactors = FALSE)
df1$Quarter <- rownames(df1)
df1$Country <- ""

df2 <- as.data.frame(table2, stringsAsFactors = FALSE)
df2$Quarter <- rownames(df2)
df2$Country <- ""

df3 <- as.data.frame(table3, stringsAsFactors = FALSE)
df3$Quarter <- rownames(df3)
df3$Country <- ""




# This function adds a blank header row with only the country name
add_country_row <- function(data, country_name) {
  # Ensure the correct column order of "Country", "Quarter", and the rest of the columns names (years)
  correct_order <- c("Country", "Quarter", setdiff(names(data), c("Country", "Quarter")))
  
  # Create a blank row with the correct column order
  header <- as.data.frame(matrix("", ncol = length(correct_order), nrow = 1))
  colnames(header) <- correct_order
  
  # Add the country name to the "Country" column
  header[1, "Country"] <- country_name
  
  # Ensure the data also follows the correct column order
  data <- data[, correct_order]
  
  # Combine the header row with the data
  return(rbind(header, data))
}

# Apply the function to each country's data
df1Withcountry <- add_country_row(df1, unitsCountry1)
df2WithCountry <- add_country_row(df2, unitsCountry2)
df3Withcountry <- add_country_row(df3, unitsCountry3)

# Combine all tables into one
finalTable <- rbind(df1Withcountry, df2WithCountry, df3Withcountry)

# Display the updated table with headers
finalTable %>%
  kbl(row.names = FALSE, # Suppress row indices
      col.names = c("", "", "2005", "2006", "2009", "2010", "2011", "2012", "2013", "Total", "Average"),
      caption = "Number of units sold by country for past three years.",
      align = "c") %>%
  add_header_above(setNames(11, "Year")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE) %>%
  row_spec(0, bold = TRUE, font_size = 14) %>%
  column_spec(1, bold = TRUE)


```



## Summary and Recommendations

Based on the available data, the analysis of Media Distributors, Inc.’s film and music sales reveals a robust revenue generation pattern, with `r country1` and the `r country2` emerging as the primary contributors to the company’s total sales. Between `r firstYear` and `r lastYear`, sales peaked in `r HighestSalesData$YEAR`, with total revenue reaching \$`r format(HighestSalesData$RevenuePerYear, big.mark = ",")` across both business units. Films have contributed more to the totl revenue as compared to Music. The revenue by Films is concentrated in the years 2005 and 2006, whereas rest of the years Music has contibuted to the revenue. Sales patterns fluctuate by quarter and geography. The customer base is concentrated in `r customerCountry1`, `r customerCountry2`, and `r customerCountry3`, which also serve as the top-performing markets.

Despite these strengths, Media Distributors, Inc. faces challenges related to its siloed information systems. With plans for acquisition, the company must present a cohesive and integrated business view to appeal to potential buyers. With nearly `r format(totalCustomers$totalCustomers, big.mark = ",")` customers across `r format(totalCountries$totalCountries, big.mark = ",")` countries, Media Distributors should invest in customer relationship management (CRM) tools to personalize outreach and foster loyalty. Segmenting customers by preferences (film or music) and spending habits can optimize targeting.



```{r disconnectFromDB, echo = F, warning = F, message = F, results = "hide"}
dbDisconnect(conn)

# Citations: --------------------------------------------------------------
## course materials: 
## https://northeastern.instructure.com/courses/206139/modules
## R documentation multiple pages: 
## https://www.rdocumentation.org/
## Used Claude to understand tables and plotting with real world examples in R for SQL
## GeeksForGeeks gfg multiple pages: 
## https://www.geeksforgeeks.org/learn-r-programming/
```